---
title: "Housing Values in Suburbs of Boston"
author: "JV"
date: "16/11/2020"
output: ioslides_presentation
smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
Reproducible pitch presentation for the final project of Coursera Developing Data Science Tools course [Data Science Specialization - Course N9]. This document will go over the basics of developing the Shiny app. For more information please see the following links:

1. The Boston Housing Dataset (Boston dataset) can be accessed throught **library(MASS)** in R
3. The GitHub repository that containing the R codes required to build the Shiny App (**server.R** and **ui.R**) can be accessed [here](https://github.com/jgvelascoo/DevelopingDataProductsR)
2. The Shiny app can be accessed [here](https://jvelascoo.shinyapps.io/BostonDatasetApp/), which contains
  - Distribution of each variable throught a histogram
  - Relationship of up to three variables throught a scatter plot

## The Boston Dataset {.smaller}
- Use **?Boston** to read more about the study
```{r, echo = T}
library(MASS)
summary(Boston)
```

## Codes for Histogram {.smaller}
```{r, echo = T}
inputVar <- 'medv'; inputBin <- 25; histVal <- Boston[, inputVar]
hist(histVal, breaks = seq(min(histVal), max(histVal), length.out = inputBin+1),
     xlab = inputVar, main = paste('Distribution of', inputVar),
     col = 'darkgray', border = 'white')
```

## Codes for Scatter Plot {.smaller}
```{r, echo = T, fig.width=6, fig.height=3.9, fig.align = 'center'}
library(ggplot2)
scatX <- 'crim'; scatY <- 'medv'; scatC <- 'age'
ggplot(data = Boston, aes(x = crim, y = medv, color = age)) + 
      geom_point() + xlab(scatX) + ylab(scatY) + labs(colour = scatC) +
      ggtitle(paste('Scatter plot of', scatX, 'vs', scatY)) +
      theme(plot.title = element_text(hjust = 0.5))
```

